---
title: "week9-task2"
author: "Satie Airame"
date: "12/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(broom)
```

## Read in data

```{r}
lizards <- read_csv(here("data", "lizards.csv"))
```

## Counts of lizards by species

```{r}
lizards %>%
```


```{r}
count(spp) %>% 
  arrange(-n)
```

## Make a subset

- UTST lizards only
- Sites: IBPE (enclosure grassland), RABB (rabbit mesquite site), "EAST" (east tarbush site)
- Tail condition is recorded (W = whole, B = broken)

```{r}
utst <- lizards %>% 
  filter(spp == "UTST") %>% 
  filter(site %in% c("IBPE", "RABB", "EAST")) %>% 
  filter(tail %in% c("W", "B"))
```

## Find counts (using dplyr) and proportions of lizards with broken or whole tails at each site

```{r}
utst %>% 
  count(site, tail)
```
## Use tabyl (in janitor) into table format, easier to understand and compare across groups.

```{r}
tail_counts <- utst %>% 
  janitor::tabyl(site,tail)

tail_proportions <- tail_counts %>% 
  janitor::adorn_percentages() %>% # look at the percentages (not n)
  janitor::adorn_pct_formatting(digits = 2) %>% # round to 2 sig digits
  janitor::adorn_ns() # include actual counts
```

## Is there a significant difference between lizards with broken tails and whole tails at three different sites?

## Convert to contingency table (convert site => rowname)

Use 'column_to_rownames()'.

```{r}
lizard_ct <- tail_counts %>% 
  column_to_rownames(var = "site") # use quotes to remove as a variable and use inputs as a rowname
```
 ## Run Chi-square
 
 Are tail breakage and site indepedent?
 
```{r}
lizard_x2 <- chisq.test(lizard_ct)
lizard_x2

lizard_tidy <- broom::tidy(lizard_x2)
```


There is a significant association (i.e., non-independence) between site and lizard tail breakage ($/chi$^2^('r lizard_tidy$parameter') = 'r lizard_tidy$statistic', *p* = 'r lizard_tidy$p.value').


































